Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-06-08 PaperBCJ.tex

\section{Matherials and Methods}
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
For the stages of obtaining images and training net we  used the following elements: A Raspberry Pi 3 with Pi Camera V2.1 for the record of images, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing. Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
\\

>>>>

\section{Matherials and Methods}
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image recording, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing. Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
\\
